---
title: "Project3: Chicken or Dogs?"
author: "Group 14"
date: "March 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,warning=FALSE}
if(!require("gbm")){
  install.packages("gbm")
}

if(!require("data.table")){
  install.packages("data.table")
}

library("gbm")
library("data.table")

source('../lib/cross_validation.R')
source("../lib/train_GBM.R")
#source("../lib/train_ADV.R")##Yi: need to be written, very important, uncomment it after you write it.
```

###Step0: Set directories
```{r}
experiment_dir <- "../data/" # This will be modified for different data sets.
img_train_dir <- paste(experiment_dir, "train/", sep="")
img_test_dir <- paste(experiment_dir, "test/", sep="")
```

### Step 1: set up controls for evaluation experiments.

we use some controls for the evaluation experiments. 

+ (T/F) cross-validation on the training set
+ (number) K, the number of CV folds
#+ (T/F) process features for training set
+ (T/F) run evaluation on an independent test set

```{r exp_setup}
run.cv=TRUE # run cross-validation on the training set
K <- 5  # number of CV folds
run.test=TRUE # run evaluation on an independent test set
```

### Step 2: import training images class labels.
```{r}
label_train <- read.table(paste(experiment_dir, "labels.csv", sep=""),
                          header=T)
label_train<-as.matrix(label_train)

label_test<-mylabels[label_test_num,]#need to be changed based on professor's data***
label_test<-as.matrix(label_test)

sift_features_train<-read.csv("../data/sift_features.csv")
sift_features_train<-t(sift_features_all)
sift_features_train<-as.matrix(sift_features_all)

```

###Step 3: Fit training data into GBM Model, which is our baseline model. And then make predictions on test data set.

Run Cross Validation on different shrinkage parameters, here we take parameters from 0.1 to 5 step 0.1

```{r,warning=FALSE}
shrinks<-seq(0.1, 0.5, 0.1)
#record the test error for GBM with diffrent shrinkage parameters
test_err_GBM = numeric(length(shrinks))
for(i in 1:length(shrinks)){
  cat("GBM model Cross Validation No.", i, "model out of",length(shrinks), "models", "\n")

    paras = list(depth=1,
             shrinkage=shrinks[i],
             n.trees=100)

  test_err_GBM[i] = cross_validation(sift_features_train, label_train, paras=paras, K=5, model='GBM')
}
```

*Plot the test error
```{r}
plot(y=test_err_GBM,x=shrinks,xlab="shrinkages",ylab="CV Test Error",main="GBM CV Test Error",type="n")
points(y=test_err_GBM,x=shrinks, col="blue", pch=16)
lines(y=test_err_GBM,x=shrinks, col="blue")
```


* find the best shrinkage parameters and fit it into GBM Model
```{r}
best_shrink = shrinks[which.min(test_err_GBM)]
paste("The best shrinkage parameter is",best_shrink)
best_paras = list(depth=1, shrinkage=best_shrink, n.trees=100)
```


* train the model with the entire training set under best parameters
```{r}
tm_GBM<-NA
tm_GBM <- system.time(GBM_fit<-train_GBM(x=sift_features_train, y=label_train, paras=best_paras))
```

*fit test sift features into trained GBM model and predict the results. Then save prediction in output folder, both in csv and Rdata
```{r}
pred_GBM<-test(GBM_fit,sift_features_test)
write.csv(pred_GBM,file="../output/GBM_prediction.csv")
save(pred_GBM,file="../output/GBM_prediction.Rdata")
pred_accuracy<-mean(pred_GBM==label_test)
```

###Step 4: Fit training data into Advanced Model
Input:load train images' CNN features
Output: fitted advanced model

###Step 5: Make Prediction based on Advanced Model
will use function in "test.R"

GBM:
Input:sift features for test images (Professor may provide it, I will check with TA)
Output:0/1
Also accuracy of the prediction

ADV:
Input:test images CNN features
Output:0/1

### Summarize Running Time
```{r}
cat("Time for training model=", tm_GBM [1], "s \n")
```


